Recalibrating Gravitational Wave Phenomenological Waveform Model

### 2023-03-13 src/tex/ms.tex
update

From Eq. \ref{eq:Lambda}, we can see that the values of $\lambda$ are
fundamental to waveform generation, which can significantly affect the shape of
final waveforms. Thus, having a set of accurate waveform coefficients is
important. Generally, waveform coefficients are obtained by calibrating with NR
waveforms, which are waveforms computed using NR simulations. In the case of
\citep{khan2016frequency}, $\lambda$ were obtained by fitting model-generated
waveforms to NR waveforms. For each NR simulation, they can obtain one set of
$\Lambda$'s through optimization. With many sets of $\Lambda$, $\lambda$ are
subsequently found by fitting against Eq. \ref{eq:Lambda}. However, this
piece-wise fitting deployed by \citep{khan2016frequency} causes calibrated
coefficients to have systematic biases. Since coefficients were not fitted
jointly, correlations between segments are omitted. Hence, the model introduces
systematic biases to $\lambda$ and will be accumulated and passed along to the
data analysis pipeline. Also, their calibration procedure does not guarantee to
have the optimal set of $\lambda$, since the process of connecting segments
alters the previously fitted waveform. The model-generated waveforms do not take
this effect into account, and thus introduces additional inaccuracies.

>>>>

\kw{Need to work on this paragraph}
From Eq. \ref{eq:Lambda}, we can see that the values of $\lambda$ are
fundamental to waveform generation, which can significantly affect the shape of
final waveforms. Thus, having a set of accurate waveform coefficients is
important. Generally, waveform coefficients are obtained by calibrating with NR
waveforms, which are waveforms computed using NR simulations. In the case of
\citep{khan2016frequency}, $\lambda$ were obtained by fitting model-generated
waveforms to NR waveforms. For each NR simulation, they can obtain one set of
$\Lambda$'s through optimization. With many sets of $\Lambda$, $\lambda$ are
subsequently found by fitting against Eq. \ref{eq:Lambda}. Since the fitting
procedure is done in a piece-wise manner, the correlations between different
segments are omitted, which could limit the accuracy of the model. Also,
their calibration procedure does not guarantee to have the optimal set of
$\lambda$, since the process of connecting segments alters the previously fitted
waveform. The model-generated waveforms do not take this effect into account,
and thus introduces additional inaccuracies.
